Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-11 method.tex
Filters are implicitly real-valued
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1020 ccdd05d5-56c1-461a-bf98-85f6876523b4
Slight rewording
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1021 ccdd05d5-56c1-461a-bf98-85f6876523b4
Reordered section 2.1 in a more sensible way
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1022 ccdd05d5-56c1-461a-bf98-85f6876523b4

Inspiral signals are continuously parameterized by a set of intrinsic source
parameters $\mathbf\Theta$ that determine the amplitude and phase evolution of the
\GW{} strain. For systems in which the effects of spin can be ignored, the intrinsic
source parameters are the just component masses of the binary,
 $\mathbf\Theta = (m_1, m_2)$. For a given source, the strain observed by the
 detector is a linear combination of two waveforms corresponding to the
`$+$' and `$\times$' \GW{} polarizations.  Thus, for any value of
$\mathbf\Theta$ we must implement two filters (real-valued) filters.

Searches for inspiral signals typically employ matched filter
banks that discretely sample the possible intrinsic parameters~\citep{findchirppaper}.
To construct a template bank, templates are chosen with
$\numtmps/2$ discrete signal parameters $\mathbf\Theta_0,\, \mathbf\Theta_1,\, \dots,\,
\mathbf\Theta_{\numtmps/2-1}$ to assure a bounded loss of \SNR\ for signals given by
intermediate values of the intrinsic parameters~\citep{Owen:1998dk}. That
is, any possible signal within a given range of intrinsic
source parameters will have an inner product that is $\geqslant 0.97$ with at
least one template. Such a template bank is said to have a {\em minimum match}
of 0.97.

Filtering the detector data involves a convolution of the data with the
templates.  For a unit-normalized template $h_i[k]$ and whitened detector data
$x[k]$, both sampled at a rate $f^0$, the result can be interpreted as the
\SNR{}, $\rho_i[k]$ defined as
%
% Filtering equations
%
\begin{equation}
	\label{eq:SNRTD}
	\rho_i [k] = \sum_{n=0}^{N-1} h_{i}[n] x [k-n].
\end{equation}
The coefficients for the $\numtmps$ filters are known as templates, 
and are formed by discretizing and time reversing the
waveforms and weighting them by the inverse amplitude spectral density of the
detector's noise. The data from the detector are whitened and convolved with each
template to produce $\numtmps$ \SNR\ time series. Local peak-finding across time and
templates determines detection candidates.

>>>>

Inspiral signals are continuously parameterized by a set of intrinsic source
parameters $\mathbf\Theta$ that determine the amplitude and phase evolution of the
\GW{} strain. For systems in which the effects of spin can be ignored, the intrinsic
source parameters are the just component masses of the binary,
 $\mathbf\Theta = (m_1, m_2)$. For a given source, the strain observed by the
 detector is a linear combination of two waveforms corresponding to the
`$+$' and `$\times$' \GW{} polarizations.  Thus, we must design two filters
for each $\mathbf\Theta$.

Searches for inspiral signals typically employ matched filter
banks that discretely sample the possible intrinsic parameters~\citep{findchirppaper}.
The coefficients for the $\numtmps$ filters are known as templates, 
and are formed by discretizing and time reversing the
waveforms and weighting them by the inverse amplitude spectral density of the
detector's noise.
To construct a template bank, templates are chosen with
$\numtmps/2$ discrete signal parameters $\mathbf\Theta_0,\, \mathbf\Theta_1,\, \dots,\,
\mathbf\Theta_{\numtmps/2-1}$. These are chosen such that any possible signal
will have an inner product $\geqslant 0.97$ with at least one template.
Such a template bank is said to have a {\em minimum match} of 0.97~\citep{Owen:1998dk}.

Filtering the detector data involves a convolution of the data with the
templates.  For a unit-normalized template $h_i[k]$ and whitened detector data
$x[k]$, both sampled at a rate $f^0$, the result can be interpreted as the
\SNR{}, $\rho_i[k]$ defined as
%
% Filtering equations
%
\begin{equation}
	\label{eq:SNRTD}
	\rho_i [k] = \sum_{n=0}^{N-1} h_{i}[n] x [k-n].
\end{equation}
This results in $\numtmps$ \SNR\ time series. Local peak-finding across time and
templates determines detection candidates.
